Figure 4a

### 2018-03-05 inst/coding_potential_cpat/coding_potential_cpat.Rmd
fixing headers in Rmds
re-ran all rmds and added sessionInfo to all
all paths updated to match article inc. Rmd titles
fixing supplementary names in file map and Rmds
all verbose changes finished before review

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"

####_Introduction_

@@

url <- fileMap(type = "rds")["figure1f"][[1]]
cpat <-read_rds(url(file.path(dataUrl, url)))
cpat

@@

*Results for Coding-potential Calculator are located in Supplementary figure 1g.

>>>>

#### _Introduction_

@@

cpat <- getData("Figure 1f")
cpat

@@

*Results for Coding-potential Calculator are located in Supplementary Figure 2e.

### 2018-03-05 inst/hct116_p53_null/hct116_p53_null.Rmd
fixing supplementary names in file map and Rmds
all verbose changes finished before review

#library(grDevices)
```

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"

@@

url <- fileMap(type = "rds")["Figure 2b"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

<div class="caption">
Monitoring the effects of 24 hours doxorubicin treatment on miR34a asRNA and HG in P53+/+ and p53-/- HCT116 cells. The points represent the values obtained from each independant experiment (n = 3) whereas, the gray shadow represents the distribution of those points. 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.
</div>

>>>>

@@

data <- getData("Figure 2b")

@@

<div class="caption">
Monitoring the effects of 24 hours doxorubicin treatment on miR34a asRNA and HG in P53+/+ and p53-/- HCT116 cells. The points represent the values obtained from each independant experiment (n = 3). 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.
</div>

### 2018-03-05 inst/isoforms/isoforms.Rmd
fixing supplementary names in file map and Rmds
all verbose changes finished before review

---
title: "Figure 1-Supplement 2c"
subtitle: "miR34a asRNA isoform cloning"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

Primer combinations:
miR34a AS F12 + miR34a AS R1
miR34a AS F12 + miR34a AS R2
miR34a AS F12 + miR34a AS R3
miR34a AS F12 + miR34a AS Ex3 R1 (56 degrees annealing)
miR34a AS F12 + miR34a AS Ex3 R1 (58 degrees annealing)

@@

url <- fileMap(type = "png")["Figure 1-Supplement 2c"][[1]]
knitr::include_graphics(file.path(projectUrl, url))

>>>>

---
title: "Supplementary Figure 2c"
subtitle: "miR34a asRNA isoform cloning"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

@@

Primer combinations:

miR34a AS F12 + miR34a AS R1  
miR34a AS F12 + miR34a AS R2  
miR34a AS F12 + miR34a AS R3  
miR34a AS F12 + miR34a AS Ex3 R1 (56 degrees annealing)  
miR34a AS F12 + miR34a AS Ex3 R1 (58 degrees annealing)

@@

url <- fileMap(type = "png")["Supplementary Figure 2c"][[1]]
knitr::include_graphics(file.path(projectUrl, url))

### 2018-03-05 inst/mir34a_locus/mir34a_locus.Rmd
fixing headers in Rmds
all paths updated to match article inc. Rmd titles
all verbose changes finished before review

url <- fileMap(type = "png")["figure1a"][[1]]
knitr::include_graphics(file.path(projectUrl, url))

@@

####_Conclusion_

GENCODE annotation supports the presence of a transcript orininating in the antisense orientation from the miR34a gene.

>>>>

url <- fileMap(type = "png")["Figure 1a"][[1]]
knitr::include_graphics(file.path(projectUrl, url))

@@

#### _Conclusion_

Refseq annotation supports the presence of a transcript orininating in the antisense orientation from the miR34a gene.

### 2018-03-05 inst/p1_hct116_hek293t/p1_hct116_hek293t.Rmd
all verbose changes finished before review

*For a schematic representation of the P1 construct please see Figure 2-Supplement 1a-b.

@@

<div class="caption">
miR34a asRNA and miR34a HG levels in HCT116 and HEK293t cells after transfection with P1 or empty constructs. Luciferase represents miR34a HG and renilla represents miR34a asRNA. The points represent the values obtained from each independant experiment (n = 3) whereas, the gray shadow represents the distribution of those points. 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.
</div>

>>>>

*For a schematic representation of the P1 construct please see Supplementary Figure 3a-b.

@@

<div class="caption">
miR34a asRNA and miR34a HG levels in HCT116 and HEK293t cells after transfection with P1 or empty constructs. Luciferase represents miR34a HG and renilla represents miR34a asRNA. The points represent the values obtained from each independant experiment (n = 3). 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.
</div>

### 2018-03-05 inst/p1_shrna_renilla_dox/p1_shrna_renilla_dox.Rmd
all verbose changes finished before review

See Figure 2c for a schematic representation of the P1 construct.

@@

<div class="caption">
HCT116 cells were co-transfected with the p1 construct and shRNA renilla or shRNA control and subsequently treated with increasing doses of doxorubicin. 24 hours post-treatment, cells were harvested and renilla and luciferase levels were measured using QPCR. Statistical testing compared the shRNA control with shRNA renilla transfected cells using the respective treatment condition. The points represent the values obtained from each independant experiment (n = 3) whereas, the gray shadow represents the distribution of those points. 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown.
</div>

>>>>

See Supplementary Figure 3a-b for a schematic representation of the P1 construct.

@@

<div class="caption">
HCT116 cells were co-transfected with the p1 construct and shRNA renilla or shRNA control and subsequently treated with increasing doses of doxorubicin. 24 hours post-treatment, cells were harvested and renilla and luciferase levels were measured using QPCR. Statistical testing compared the shRNA control with shRNA renilla transfected cells using the respective treatment condition. The points represent the values obtained from each independant experiment (n = 3). 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown.
</div>

### 2018-03-05 inst/primer_walk/primer_walk.Rmd
fixing headers in Rmds
re-ran all rmds and added sessionInfo to all
all paths updated to match article inc. Rmd titles
all verbose changes finished before review

####_Results_

Primer placement at the locus can be viewed in Supplementary Figure 1b.

@@

url <- fileMap(type = "png")["figure1e"][[1]]
knitr::include_graphics(file.path(projectUrl, url))

@@

####_Conclusion_

It appears as though the miR34a asRNA transcript start site is somewhat upstream of the annotated start site. Although there is some product present for the F12 primer, the majority of transcription seems to be originating from the F11 primer. This indicates that the start site is between 71-224bp upstream of the annotated start site.

>>>>

#### _Results_

Primer placement at the locus can be viewed in Supplementary Figure 2a.

@@

url <- fileMap(type = "png")["Figure 1e"][[1]]
knitr::include_graphics(file.path(projectUrl, url))

@@

#### _Conclusion_

It appears as though the miR34a asRNA transcript start site is somewhat upstream of the annotated start site. Although there is some product present for the F12 primer, the majority of transcription seems to be originating from the F11 primer. This indicates that the start site is between 90-224bp upstream of the annotated start site.

### 2018-03-05 inst/tcga_survival/tcga_survival.Rmd
all verbose changes finished before review

```{r, warning = FALSE}
#Add the colors for the plot to the data
colors <- getCancerColors()
survData <- full_join(survData, colors, by = "cancer")

>>>>

```{r, warning = FALSE, fig.align='center', fig.height=8, fig.width=12}
#Add the colors for the plot to the data
colors <- getCancerColors()
survData <- full_join(survData, colors, by = "cancer")

### 2018-03-05 inst/tcga_survival_short/tcga_survival_short.Rmd
all verbose changes finished before review

---
title: "Figure 4a and Supplementary Figure 5"
subtitle: "Survival curves"
author: "Jimmy Van den Eynden and Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

@@

<div class="col2">
```{r}
trash <- pmap(
  list(independant$data, independant$surv.fit, independant$gene, independant$cancer, independant$p.value), 
  function(v, w, x, y, z) {
    plotKM(v, w, x, y, z)
  }
)
```
</div>

>>>>

---
title: "Figure 4a"
subtitle: "Survival curves"
author: "Jimmy Van den Eynden and Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

@@

```{r, fig.align='center', fig.height=8, fig.width=12}
independant <- filter(independant, cancer == "KIRP")
trash <- pmap(
  list(independant$data, independant$surv.fit, independant$gene, independant$cancer, independant$p.value), 
  function(v, w, x, y, z) {
    plotKM(v, w, x, y, z)
  }
)
```
